Autogenerated Questions Paper Draft

### 2018-04-09 paper_draft/paper_draft.tex
Add info about GIFT and moodle

\section{Problem Description (needs work)}
For any large introductory undergraduate course, testing becomes virtually impossible on a (clerical?) level, especially for a small examination
such as an in-class quiz. However, technology allows instructors to develop and distribute exams in an online environment,
easing the arduous task of passing out and collecting paper exams. However, extra problems are presented with online tests (especially those
without a proctor), such as authentication, blah, and most importantly cheating (reference). Some solutions have been discussed before (reference),
but problems still remain. In an effort to prevent cheating, instructors may use different questions for different students, but the task of creating exam
questions (let alone multiple ones) has been noted to be very intensive and time-consuming (reference). A possible solution to this problem has been
presented by (reference), but this implementation is in the somewhat narrow field of pharmacology, and it doesn't discuss important details such as
the methods for generating distractors or the affect of randomness on each question -- which may be of interest to some as it can affect difficulty and
the objective of some questions. Furthermore, there is no discussion of the reusability or additions of the system, making it seem completely isolated
and specific [VERFIY THESE POINTS].

@@

Once the program has finished, all output files generated in .txt format containing the GIFT-formatted questions, and they can be uploaded
directly to the Moodle course with no extra effort. Each category is contained in its own file, and any
difficulties selected within the category are automatically separated into their own question banks, allowing
for exam questions to be selected by difficulty.

@@

>>>>

\section{Problem Description (needs work)}

Maybe this is closer to an abstract style?

For any large introductory undergraduate course, testing becomes virtually impossible on a (clerical?) level, especially for a small examination
such as an in-class quiz. However, technology allows instructors to develop and distribute exams in an online environment,
easing the arduous task of passing out and collecting paper exams. However, extra problems are presented with online tests (especially those
without a proctor), such as authentication, blah, and most importantly cheating (reference). Some solutions have been discussed before (reference),
but problems still remain. In an effort to prevent cheating, instructors may use different questions for different students, but the task of creating exam
questions (let alone multiple ones) has been noted to be very intensive and time-consuming (reference). A possible solution to this problem has been
presented by (reference), but this implementation is in the somewhat narrow field of pharmacology, and it doesn't discuss important details such as
the methods for generating distractors or the relative difficulty of the questions. Furthermore, there is no discussion of the reusability or additions of the system, making it seem completely isolated
and specific [VERFIY THESE POINTS].

In this paper, we propose a system to be used for introductory programming classes at the undergraduate level, with a focus on syntax, control structures, and logic used in C++. This system offers a number of different categories, each with different levels of difficulty, that focus on fairly testing students. The

@@

Once the program has finished, all output files generated in .txt format containing the GIFT-formatted questions, and they can be uploaded
directly to the Moodle course with no extra effort. Each category is contained in its own file, and any
difficulties selected within the category are automatically separated into their own question banks, allowing
for exam questions to be selected by difficulty (this functionality is handled by Moodle).

@@

The reason we have chosen GIFT as the output markup language to these questions -- as opposed to HTML or XML -- is for a number of reasons: 1) this language was constructed specifically for use in our current course management system (CMS) Moodle [TODO: add footnote for moodle/GIFT here]; 2) GIFT has very minimal syntax, which allows it to be easily parsed and read by humans, which is useful when quickly evaluating the questions; and 3) similar to other courses [TODO: maybe reference here?], the instructors of this paper require students to construct their own multiple choice questions that may be used in a real exam. (TODO: should I mention this last point?) The reason we chose Moodle is because of its support through our instituiton. (should I mention this either?)
